---
title       : Shiny App on Mtcars
subtitle    : Very first app
author      : dylan.woon
job         : novice data explorer
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow     # 
widgets     : [quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---

## Why Shiny App on Mtcars?

1. Car is common - anyone can explore the apps and data without prior research
2. Great data quality - utilizing R's built in datasets
3. Demonstrate the value of K Means Clustering - when applied tactfully

- Mtcars dataset - https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html

--- 

## Really quick rCharts on mtcars

```{r, echo = F, results = "asis"}
require(rCharts)
```

```{r, echo = T, results = "asis"}
n1 <- nPlot(mpg ~ disp, group = "cyl", type = "multiBarChart", data = mtcars)
n1$print("chart1")
```

---

## Can you identify hidden patterns within the app?

- By varying the variables and number of clusters in the Shiny app, certain patterns may be discovered.
- There's no right or wrong answer
- It's fine even if no hidden patterns are discovered. Data science is largely about experimentation

--- &radio

## Quiz

Is K Means Clustering used on regression or classification problems?

1. _Classification_ 
2. Regression
3. None of above

*** .hint
Clustering is the task of grouping a set of objects.

*** .explanation
In machine learning, classification is the used to identify to which of a set of categories a new observation belongs, on the basis of a training set of data with known category membership.


